Apache Flink\texttrademark: Stream and Batch Processing in a Single Engine

### 2016-05-30 paper.tex
Updates from ShareLaTeX

\author{Paris Carbone\textsuperscript{$\dagger$} \\ Asterios Katsifodimos\textsuperscript{*} \\\\ \small{ \textsf{\small \textsuperscript{$\dagger$}KTH \& SICS Sweden}} \\ \small \href{parisc,haridi@kth.se}{parisc,haridi@kth.se}
\and Stephan Ewen\textsuperscript{$\ddagger$} \\ Volker Markl\textsuperscript{*} \\\\ \small \textsf{\textsuperscript{$\ddagger$}data Artisans} \\ \small \href{first@data-artisans.com}{first@data-artisans.com}
\and Seif Haridi\textsuperscript{$\dagger$} \\ Kostas Tzoumas\textsuperscript{$\ddagger$} \\\\ \small \textsf{\textsuperscript{*}TU Berlin} \\ \small \href{fist.last@tu-berlin.de}{first.last@tu-berlin.de}
%
\vspace{-5mm}
}

>>>>

\author{Paris Carbone\textsuperscript{$\dagger$} \\ Asterios Katsifodimos\textsuperscript{*} \\\\ \small{ \textsf{\small \textsuperscript{$\dagger$}KTH \& SICS Sweden}} \\ \small \href{parisc,haridi@kth.se}{parisc,haridi@kth.se}
\and Stephan Ewen\textsuperscript{$\ddagger$} \\ Volker Markl\textsuperscript{*} \\\\ \small \textsf{\textsuperscript{$\ddagger$}data Artisans} \\ \small \href{first@data-artisans.com}{first@data-artisans.com}
\and Seif Haridi\textsuperscript{$\dagger$} \\ Kostas Tzoumas\textsuperscript{$\ddagger$} \\\\ \small \textsf{\textsuperscript{*}TU Berlin \& DFKI} \\ \small \href{fist.last@tu-berlin.de}{first.last@tu-berlin.de}
%
\vspace{-5mm}
}
